%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\renewcommand{\labelitemi}{--}
\usepackage{comment, amsmath, amssymb, fontawesome}

\usepackage[scale=0.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\firstname{Aaron}
\familyname{Niskin}

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
% \address{3415 Chase Ave}{Miami Beach, FL 33140}
%\mobile{(305) 575 9217}
\phone{(305) 894-6475}
\email{aaron@niskin.org}
\homepage{www.aaron.niskin.org}{aaron.niskin.org}
%\homepage{http://www.github.com/amniskin}{github.com/amniskin}
%\github{amniskin}
\linkedin{/in/aaron-niskin}
\github{amniskin}
% \extrainfo{\httplink{linkedin.com/in/aaron-niskin}}
%\photo[70pt][0.4pt]{pictures/DSC_0016.JPG} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}



\begin{document}

%%% {{{ Cover Letter
\begin{comment}
	%----------------------------------------------------------------------------------------
	%	COVER LETTER
	%----------------------------------------------------------------------------------------

	% To remove the cover letter, comment out this entire block

	\recipient{HR Department}{BlackRock\\40 East 52nd Street \\10022 New York, NY} % Letter recipient
	\date{\today} % Letter date
	\opening{Dear Sir or Madam,} % Opening greeting
	\closing{Sincerely yours,} % Closing phrase
	\enclosure[Attached]{Resum\'e} % List of enclosed documents

	\makelettertitle % Print letter title
	%Ever since  My interest in BlackRock was piqued by my professor, Dr. Gary Kalmanovich, told me about Jacopo Dalmasso, a recent graduate from NCF who applied machine learning to a real world problem at BlackRock, and the internship possibility at BlackRock.
	When my professor, Dr. Gary Kalmanovich, first told me about Jacopo Dalmasso's research with BlackRock, my interest in BlackRock solidified. Some people find satisfaction in learning a thing and sticking with it. I am not one of those people. I prefer to live on the edge of my own understanding, constantly venturing further into the unknown. This outlook has resulted in my taking nearly every Math course FIU had to offer, and my interest in entering the field of Finance. This preference is not solely for personal growth; it has also led to many workplace improvements.

	As an example, I recall one instance from my Army days. For several missions, we would perform our standard pre-mission communications checks without any issues, but later on we would find ourselves unable to communicate. Our Commo Sergeant said these were unavoidable phenomena, which didn't sound reasonable to me. I (a Private at the time) conducted my own investigation. It turns out that these radios have to be synced in order to communicate (a cryptographic necessity), and when portions of the unit were separated by land barriers for a few minutes they would fall out of sync. I discovered that this, being a known problem, has a solution and I re-engineered our company radios and we never had that problem again.

	%which is to say that they change frequency according to a predetermined sequence and the time. The time, however, is the crux. Each time a radio ``que's the mic'', a receiving radio's time is synced to the sender. If, as was the case with us, two radios are separated for a few minutes by a land barrier, it's likely that net will be split due to the random drift. I discovered that this, being a known problem, has a solution and I re-engineered our company radios and we never had that problem again.

	I believe my penchant for learning, problem solving, and optimization would make me a valuable member of the BlackRock team. I expect the work to be challenging, but I am motivated by challenges. I am looking forward to late nights with textbooks and my computer, finding ways to optimize code, etc.

	Thank you very much for your time and consideration. If you have any questions and or comments, please feel free to contact me at any time.

	\makeletterclosing % Print letter signature

	\clearpage

\end{comment}
%%% }}}
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%%% {{{ Skills/Languages
\section{Skills and Languages}
\cvitem{Advanced}{Spanish | \textsc{Statistical Analysis}, \textsc{Portfolio Construction}, \textsc{Signals Research}}
\cvitem{Intermediate}{Hebrew | \textsc{Programming}, \textsc{Software Design}, \textsc{Cloud Architecture}}
\cvitem{Basic}{German, Russian | \textsc{Front End Security}, \textsc{Code Optimization}}
%%% }}}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

%%% {{{ Education
\section{Education}
\cventry{2016--2018}{Master of Science In Data Science}{New College of Florida}{Sarasota}{}{}
\cventry{2012--2015}{Bachelor of Science in Mathematics \hspace{0.5em}-\hspace{0.5em} Minors in Physics and English}{Florida International University}{Miami}{}{
	%% \cvlistdoubleitem{Graduated Cum Laude \textit{GPA -- 3.64 (3.79 in major)}}{Dean's List (6 times)}
 	\begin{itemize}
 		\item Graduated Cum Laude \textit{GPA -- 3.64 (3.79 in major)}
		\item Dean's List (6 times)
 	\end{itemize}
}  % Arguments not required can be left empty
%\cventry{2010--2011}{Associate of Arts}{Miami Dade College}{Miami}{}{
%  \begin{itemize}
%    \item Graduated with Honors \textit{GPA -- 3.74 out of 4.00}
%    \item Dean's List (5 times)
%      %\item Phi Theta Kappa Honor Society Member
%    \item Physics Award
%  \end{itemize}}
%%% }}}

%%% {{{ Selected Courses
\begin{comment}
\section{Selected Courses}
%% \cvlisttripleitem{Abstract Algebra (2 semesters)}{Algebraic Geometry}{Differential Geometry}
%% \cvlisttripleitem{Classical Mechanics (2 semesters)}{Point Set Topology}{Homology of Simplicial Complexes}
%% \cvlisttripleitem{Advanced Calculus in $\mathbb{R}^n$ (2 semesters)}{Thermodynamics}{Algorithms and Numerical Methods}
%% \cvlistdoubleitem{Algebraic Geometry}{Differential Geometry}
%% \cvlistdoubleitem{Abstract Algebra (2 semesters)}{Point Set Topology}
%% \cvlistdoubleitem{Classical Mechanics (2 semesters)}{Homology of Simplicial Complexes}
%% \cvlistdoubleitem{Thermodynamics}{Advanced Calculus in $\mathbb{R}^n$ (2 semesters)}
%% \cvlistdoubleitem{Algebraic Geometry}{Differential Geometry}
\cvlistdoubleitem{Abstract Algebra (1, 2, Algebraic Geometry)}{Real Analysis (1, 2, Differential Geometry)}
%% \cvlistdoubleitem{Abstract Algebra (1, 2)}{Advanced Calculus in $\mathbb{R}^n$ (1, 2)}
\cvlistdoubleitem{Data Storage and Retrieval}{Homology of Simplicial Complexes}
\cvlistdoubleitem{Algorithms and Numerical Methods}{Point Set Topology}
\end{comment}
%%% }}}

%%% {{{  Academic Honors
\begin{comment}
	\section{Academic Honors}

	\cvitem{}{Dean's List (6 times), Florida International University}
	\cvitem{}{Dean's List (5 times), Miami Dade College}
	\cvitem{}{Phi Theta Kappa Honor Society Membership, Miami Dade College}
	\cvitem{}{Physics Award, Miami Dade College}
\end{comment}
%%% }}}

%%% {{{  Master's Thesis
\begin{comment}
	\section{Masters Thesis}

	\cvitem{Title}{\emph{Money Is The Root Of All Evil -- Or Is It?}}
	\cvitem{Supervisors}{Professor James Smith \& Associate Professor Jane Smith}
	\cvitem{Description}{This thesis explored the idea that money has been the cause of untold anguish and suffering in the world. I found that it has, in fact, not.}
\end{comment}
%%% }}}

%%% {{{  Main Courses (With descriptions)
\begin{comment}
	\section{Main Courses Taken}
	\cventry{}{Advanced Calculus in $\mathbb{R}^n$}{(2 semesters)}{}{}{
		\begin{itemize}
			\item Differentiation and Integration in $\mathbb{R}^n$
			\item Integration on Chains
			\item Fubini's Theorem
			\item Rank Theorem, Inverse Function Theorem, Implicit Function Theorem
			\item Stokes' Theorem
		\end{itemize}}

	\cventry{}{Abstract Algebra}{(2 semesters)}{}{}{
		\begin{itemize}
			\item Group theory using Category Theory
			\item Group actions
			\item Sylow Theorems
			\item General Theory of Rings, Fields and Modules
			\item Jordan Normal Form
		\end{itemize}}

	\cventry{}{Advanced Differential Equations}{}{}{}{
		\begin{itemize}
			\item Fourier Series approximation of piecewise smooth functions
			\item Legendre Polynomials
			\item Bessel Functions
		\end{itemize}}

	\cventry{}{Complex Variables}{(Independent Study)}{}{}{
		\begin{itemize}
			\item Differentiation, line integration and path independence of line integrals in $\mathbb{C}$
			\item Euler's Formula, Disc of Convergence, Multifunctions, M\"obius Transformations, Inversion, Conformal Mappings, Riemann Sphere, Cauchy-Riemann Equations
		\end{itemize}}

	\cventry{}{Axiomatic Set Theory}{}{}{}{
		\begin{itemize}
			\item Constructed the Von Neumann Ordinals from the Axioms
			\item Constructed L and WF using the Von Neumann Ordinals
		\end{itemize}}

	\cventry{}{Methods in the History of Modern Mathematics}{}{}{}{
		\begin{itemize}
			\item Derivation of Kepler's Laws
			\item Some basic Riemannian and Pseudo-Riemannian Geometry
		\end{itemize}}

	\cventry{}{Topology}{}{}{}{
		\begin{itemize}
			\item Order, Product, Subspace, Metric and Quotient topologies
			\item Continuity, limits
			\item Connected spaces, compact spaces, limit point compactness, function spaces
		\end{itemize}}

	\cventry{}{Introduction to Differential Geometry}{}{}{}{
		\begin{itemize}
			\item Curves in $\mathbb{R}^n$
			\item Local Theory of Surfaces
			\item Intrinsic Geometry of Surfaces including, geodesics, Theorema Egregium and Theorem of Gauss-Bonnet
			\item Riemannian Manifolds, Curvature Tensor, Ricci tensor
			\item Basics on Lie groups and Lie Algebras
		\end{itemize}}

	\cventry{}{Introduction to Algebraic Geometry}{}{}{}{
		\begin{itemize}
			\item The Zariski Topology
			\item Hilbert's Nullstellensatz
			\item Co-equivalence of the category of closed affine (over k) sets and the category of affine k algebras
		\end{itemize}}

	\cventry{}{Classical Mechanics}{(2 semesters)}{}{}{
		\begin{itemize}
			\item Euler-Lagrange equations, Lagrangian Mechanics
			\item Orbital Mechanics, System Dynamics, Collisions and Scattering, Noninertial Reference Frames, Rigid Body Rotation, Coupled Oscillators Normal Coordinates, and Wave Motion.
		\end{itemize}}
\end{comment}
%%% }}}

%%% {{{  Other Relevant Courses
\begin{comment}
	\section{Other Relevant Courses Taken}
	\cvlistdoubleitem{Thermodynamics}{Mathematical Methods in Physics}
	\cvlistdoubleitem{Solid State Physics}{Number Theory}
	\cvlistdoubleitem{Mathematical Statistics}{Mathematical Logic}
	\cvlistdoubleitem{Point Set Topology}{Modern Physics (2 semesters)}
\end{comment}
%%% }}}

%%% {{{ Experience
\section{Experience}
%%% {{{ Finance
\subsection{Finance}
\cventry{2018-Present}{Quantitative Researcher}{\textsc{BlackRock Inc.}}{San Francisco, CA}{Systematic Active Equity}{
	\begin{itemize}
		\item Implemented signals using a wide variety of algorithms including Linear Models, GBM, Neural Networks, KNN, etc.
		\item Implemented contextual embeddings (e.g. Bert, GPT-3, etc.) for various NLP tasks.
		\item Researched and put into production signals driving over \$100M of daily trades.
		\item Produced signals using all kinds of datasets, including alternative, fundamental, and text-based.
		\item Focused on US Equities, but conducted research for global equities markets.
		\item Focused on Stock Selection, but also conducted macro-economic, industry, country, factor-timing, and signal-combination research.
	\end{itemize}}
\cventry{2017}{Summer Analyst}{\textsc{BlackRock Inc.}}{San Francisco, CA}{Scientific Active Equity}{
	\begin{itemize}
		\item Assessed the viability of using automated machine learning for alpha generation research
		\item Developed a variable importance assessor for black box machine learning models
	\end{itemize}}
%%% }}}

%%% {{{ STEM
\subsection{STEM}
\cventry{2015--2016}{Computer Science Instructor}{\textsc{Florida Vocation Institute}}{Miami, FL}{}{
	\begin{itemize}
		\item Taught and created syllabi for several courses and created a free online course (currently live at www.fvi-grad.com)
	\end{itemize}}
\cventry{2010--2015}{Co-founder and Math/Science/Computing Tutor}{Math-Busters (www.Math-Busters.com)}{Miami, FL}{}{
	\begin{itemize}
		\item Tutored all levels of students and maintained a perfect rating with 100+ ratings and 450+ hours logged
	\end{itemize}}
%%%}}}

%%% {{{ Military
\subsection{Military}

\begin{comment}

	\cventry{2006--2009}{Infantryman}{1-38 Infantry Regiment, 4/2 ID, US Army}{Fort Lewis, WA}{}{
		\begin{itemize} %\itemsep -2pt  % reduce space between items
			\item Deployed to Iraq for OIF V from 2007-2008
			\item Combat Lifesaver, FBCB2, and other certifications
			\item Fought forest fires in Winthrop, Washington
		\end{itemize}}
	\cventry{2004--2006}{Civil Affairs Specialist}{478\textsuperscript{th} Civilian Affairs Battalion, US Army}{Perrine, FL}{}{
		\begin{itemize} %\itemsep -2pt  % reduce space between items
			\item Trained at the John F. Kennedy Special Warfare Center and School in Fort Bragg, NC for 6 months
			\item Obtained Secret Clearance
		\end{itemize}}
\end{comment}

\cventry{2004--2009}{Infantryman}{1-38 Infantry Regiment, 4/2 ID, US Army}{Fort Lewis, WA}{}{
	\begin{itemize} %\itemsep -2pt  % reduce space between items
		\item Deployed to Iraq for OIF V from 2007-2008 and fought forest fires in Winthrop, Washington
		\item Trained at the John F. Kennedy Special Warfare Center and School in Fort Bragg, NC
		\item Secret Clearance, Combat Lifesaver, FBCB2, and other certifications
	\end{itemize}}
%%%}}}
%%%}}}

\end{document}
